---
title: "06.24.2020_Work"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RPostgres)
wrds <- dbConnect(Postgres(),
                  host='wrds-pgdata.wharton.upenn.edu',
                  port=9737,
                  dbname='wrds',
                  sslmode='require',
                  user='echoi98')
library(tidyverse)
library(dbplyr)
library(caret)
library(fastDummies)
```
Link Tool
```{r}
link_tool<-read.csv("crsp_ibes_link_tool.csv",header = TRUE)
link_tool<- link_tool%>%filter(SCORE!=6)
# relevant 
link_tool<-subset(link_tool,select=-c(NCUSIP,SCORE,sdate,edate))
link_tool<-unique(link_tool)
link_tool
```
# Get Crsp Values
```{r}
# hexcd 1 = NYSE, hexcd 2 = AMEX, hexcd 3 = NASDAQ 
res <- dbSendQuery(wrds, "select date,permno,cusip,prc, ret, bid, shrout ,hexcd, cfacpr,hsiccd from crspa.msf
                   where date between '1970-12-01'
                   and '2018-12-31'")
crsp_data <- dbFetch(res, n=-1)
dbClearResult(res)
crsp_data %>% group_by(permno)
```
# Begin to process crsp_data
```{r}
crsp_data_v1<-crsp_data
# Omit values with N.A
crsp_data_v1<-na.omit(crsp_data_v1)
crsp_data_v1$year <- as.numeric(format(crsp_data_v1$date,"%Y"))
crsp_data_v1$month <- as.numeric(format(crsp_data_v1$date,"%m"))
# Find the true price by adjusting the value 
crsp_data_v1$prc <- abs(crsp_data_v1$prc)/crsp_data_v1$cfacpr
# Calculate market cap using absolute value of bid multiples by shares outstanding, factor of 1000
crsp_data_v1$market_capitalization <- crsp_data_v1$bid* crsp_data_v1$shrout
# Keep only values where price or bid is over 1 dollar 
crsp_data_v1 <-crsp_data_v1 %>% filter(prc>1||bid>1)
# Rename the columns we want 
col_order <- c("date","year", "month", "permno","price","monthly_returns","shares_outstanding","market_capitalization",'industry_code','two_digit_sich')
crsp_data_v1<- rename(crsp_data_v1, price= prc, monthly_returns=ret, shares_outstanding = shrout, exchange = hexcd, industry_code=hsiccd)
crsp_data_v1$two_digit_sich[crsp_data_v1$industry_code<1000]<-floor(crsp_data_v1$industry_code/10)
crsp_data_v1$two_digit_sich[crsp_data_v1$industry_code>=1000]<-floor(crsp_data_v1$industry_code/100)
crsp_data_v1<-crsp_data_v1[,col_order]
crsp_data_v1
```
# Remove if the return is the following values
```{r}
crsp_data_v2<-crsp_data_v1 %>% filter(monthly_returns!=-66.0|monthly_returns!=-77.0|monthly_returns!=-88.0|monthly_returns!=-99.0)
crsp_data_v2
```

IBES Pull
```{r}
res <- dbSendQuery(wrds, "select fpi,anndats,fpedats, cusip, ticker, analys, value from ibes.det_epsus
                   where fpedats between '1980-01-01' and '2019-12-31'")
ibes_pull_us<- dbFetch(res, n=-1)
dbClearResult(res)
ibes_pull_us %>% group_by()
res <- dbSendQuery(wrds, "select fpi,anndats,fpedats, cusip, ticker, analys, value from ibes.det_epsint
                   where fpedats between '1980-01-01' and '2019-12-31'")
ibes_pull_int<- dbFetch(res, n=-1)
dbClearResult(res)
ibes_pull_int %>% group_by()
IBES<-rbind(ibes_pull_us,ibes_pull_int)
IBES %>% group_by()
```
# Begin to Filter IBES Data
```{r}
IBES_v1<-IBES
IBES_v1$forecast_period_end_month<-as.numeric(format(IBES_v1$fpedats,"%m"))
IBES_v1$forecast_period_end_year<-as.numeric(format(IBES_v1$fpedats,"%Y"))
IBES_v1$analyst_year<-as.numeric(format(IBES_v1$anndats,"%Y"))
# Make sure all forecast end values are for year ending december
IBES_v1<-IBES_v1 %>% filter(forecast_period_end_month==12)
# Ensure that each forecast is for each year 
IBES_v1<-IBES_v1 %>% filter(forecast_period_end_year==analyst_year)
# filter to only get firms that can be matched 
IBES_v1<-subset(IBES_v1,select=-c(cusip))
IBES_v2<-inner_join(IBES_v1,link_tool,by =c('ticker'='TICKER'))
IBES_v2<-unique(IBES_v2)
IBES_v2 %>% group_by()
```
# Rename value
```{r}
IBES_v2<-rename(IBES_v2,f_eps=value)
```

# Save this file
```{r}
write.csv(IBES_v2 , "IBES_DATABASE.csv")
```
# Get the actual eps results 
```{r}
# Get the IBES Actual Values from US
res <- dbSendQuery(wrds, "select cusip, pends,ticker,value from ibes.act_epsus
                   where pends between '1980-01-01' and '2018-12-31'
                   and pdicity = 'ANN'
                   and cusip !=''")
ibes_actuals_us<- dbFetch(res, n=-1)
dbClearResult(res)
# Get the IBES Actual Values from INT
res <- dbSendQuery(wrds, "select cusip,pends,ticker, value from ibes.act_epsint
                   where pends between '1980-01-01' and '2018-12-31'
                   and pdicity = 'ANN'
                   and cusip !=''")
ibes_actuals_int<- dbFetch(res, n=-1)
dbClearResult(res)
ibes_actuals<-rbind(ibes_actuals_us,ibes_actuals_int)
ibes_actuals
```
Begin to filter ibes actuals
```{r}
ibes_actuals_v1<-ibes_actuals
# Dont need the cusip column
ibes_actuals_v1<-subset(ibes_actuals_v1,select=-c(cusip))
ibes_actuals_v1$period_end_month<-as.numeric(format(ibes_actuals_v1$pends,"%m"))
ibes_actuals_v1<-ibes_actuals_v1 %>% filter(period_end_month==12)
complete_ibes<-inner_join(IBES_v2,ibes_actuals_v1, by=c('ticker'='ticker','fpedats'='pends'))
complete_ibes<-rename(complete_ibes,actual_eps=value)
complete_ibes
```
# Columns we can drop 
```{r}
complete_ibes_v1<-complete_ibes
complete_ibes_v1<-subset(complete_ibes_v1,select=-c(forecast_period_end_month,forecast_period_end_year,analyst_year,period_end_month,fpi))
complete_ibes_v1
```
# Read in the Beta sheet
```{r}
beta<-read.csv("crsp_data_with_beta_portfolio_returns_export.csv",header = TRUE)
beta %>% group_by()
crsp_data_v2%>% group_by()
```
# Drop unnecessary columns
```{r}
beta_v1<-subset(beta,select=-c(X,benchmark_returns,date))
crsp_data_v3<-subset(crsp_data_v2,select=-c(shares_outstanding))
crsp_data_with_beta<-inner_join(crsp_data_v3,beta_v1,by=c('year'='year','month'='month','permno'='permno'))
crsp_data_with_beta
```
# Look at joining IBES and CRSP together
```{r}
complete_ibes_v1
crsp_data_with_beta
```
# Join by permno
```{r}
complete_ibes_v2<-subset(complete_ibes_v1,select=-c(fpedats))
complete_ibes_v2$month_analyst_predict<-as.numeric(format(complete_ibes_v2$anndats,"%m"))
complete_ibes_v2$year_analyst_predict<-as.numeric(format(complete_ibes_v2$anndats,"%Y"))
complete_data_base<-inner_join(complete_ibes_v2,crsp_data_with_beta,by=c('year_analyst_predict'='year','month_analyst_predict'='month','PERMNO'='permno'))
complete_data_base
```
# Take out columns we now dont need
```{r}
complete_data_base_v1<-subset(complete_data_base,select=-c(anndats,date))
complete_data_base_v1
write.csv(complete_data_base_v1,"pre_filter_complete_data_base_v1.csv")
```
# Begin data manipulation and filtering
```{r}
# make sure each month has a min of 3 analyst estimates
complete_data_base_v2<-complete_data_base_v1
complete_data_base_v2<-complete_data_base_v2 %>% group_by(ticker,month_analyst_predict,year_analyst_predict) %>% mutate(num_est=n_distinct(analys))
complete_data_base_v2<-complete_data_base_v2 %>% filter(num_est>=3)
# calculate the forecast standard deviation
complete_data_base_v2<-complete_data_base_v2 %>% group_by(ticker,month_analyst_predict,year_analyst_predict) %>% mutate(forecast_standard_deviation=sd(f_eps))
# calculate scaled feps by price 
complete_data_base_v2$scaled_feps<-complete_data_base_v2$forecast_standard_deviation/complete_data_base_v2$price
# calculate average forecast for each month
complete_data_base_v2<-complete_data_base_v2 %>% group_by(ticker,month_analyst_predict,year_analyst_predict) %>% mutate(average_forecasted_earnings=mean(f_eps))
complete_data_base_v2
```
# Now it does not matter which analyst estimate we take since we have the monthly averages/sd/forecast
```{r}
complete_data_base_v3<-subset(complete_data_base_v2,select=-c(analys,f_eps,PERMNO))
complete_data_base_v3<-unique(complete_data_base_v3)
complete_data_base_v3
```
# Ensure for each year we have january to december data
```{r}
complete_data_base_v4<-complete_data_base_v3
complete_data_base_v4<-complete_data_base_v4 %>% group_by(ticker,year_analyst_predict) %>% mutate(number_of_months_per_year=n_distinct(month_analyst_predict))
complete_data_base_v4<-complete_data_base_v4 %>% filter(number_of_months_per_year==12)
complete_data_base_v4
```
# Save this data down and drop columns we dont need
```{r}
complete_data_base_v5<-subset(complete_data_base_v4,select=-c(number_of_months_per_year))
complete_data_base_v5<-complete_data_base_v5%>% group_by(ticker) %>% mutate(number_of_years=n_distinct(year_analyst_predict))
write.csv(complete_data_base_v5,"data_filtered_complete.csv")
complete_data_base_v6<-complete_data_base_v5 %>% filter(number_of_years>=9)
complete_data_base_v6
write.csv(complete_data_base_v6,"data_filtered_complete_at_least_9_years_of_data.csv")
```
# Some stats 
```{r}
length(unique(complete_data_base_v4$ticker))
```




